Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-13 robdml.tex
tex

In literature, various triplet sampling strategies exist, such as random,
semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance}, and the hardest
negative sampling (\ie, the negative sample with the largest loss value).
%
Although any of them can be selected for source or destination hardness for HM,
not all the possible combinations are expected to be effective or efficient.
%
In order to figure out an empirically good combination of source and
destination hardness, we adversarially train RN18 models on the CUB dataset with
every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.

@@

As the samples will not become adversarial once $H_S>H_D$ (zero perturbation in
this case according to \cref{eq:hm}, an effective combination of source and
destination sampling strategy should make the expectation of source hardness
less than the source hardness, \ie, $E[H_S]<E[H_D]$.
%
Our empirical observation on $E[H]$ from randomly initialized
model suggests a sorting of ``random'' $<$ ``semi-hard'' $<$ ``soft-hard'' $<$
``distance'' $<$ ``hardest''.
%
Namely, the source sampling strategy should be ahead of the destination
sampling strategy in this list.

>>>>

In literature, various triplet sampling strategies exist, such as random,
semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance},
and the hardest negative sampling (\ie, the negative sample with the largest
loss value).
%
Although any of them can be selected for source or destination hardness for HM,
not all the possible combinations are expected to be effective or efficient.
%
In order to figure out an empirically good combination of source and
destination hardness, we adversarially train RN18 models on the CUB dataset
with every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.
%
Note, these methods are empirically sorted by their expectation of hardness
$E[H]$, in the ascending order: random, semihard, softhard, distance, and
hardest.

@@

As the samples will not become adversarial once $H_S>H_D$ (zero perturbation in
this case according to \cref{eq:hm}, an effective combination of source and
destination sampling strategy should make the expectation of source hardness
less than the source hardness, \ie, $E[H_S]<E[H_D]$.
%
Namely, the source sampling strategy should be ahead of the destination
sampling strategy in this list.
